Capstone Movielens Report

### 2025-11-02 reports/capstone-movielens.site/05.appendix.Rmd
RMSE.Total_kable function: hotfix.
Helper functions: refactoring.

#### [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L507) Function {#func.clamp}
\

@@

The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L507) function is shown below:
```{r eval=FALSE}
clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
```

::: {.noteblock data-latex=""}
The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L507) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L504) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L507) script on _GitHub_.
:::
:::

#### [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L521) Function {#func.msg.set_arg}
\

@@

This function is a wrapper for the [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` function, which is called internally to replace all occurrences of the pattern (placeholder) specified by the [arg_name](#func.msg.set_arg.args.arg.name) argument (`%1` by default), in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument with the value specified in the [arg](#func.msg.set_arg.args.arg) argument.

@@

The character vector returned by the internally called [stringr::str_replace_all()](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).

@@

The source code of the [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L521) function is shown below:
```{r eval=FALSE}
msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
  msg_template |> 
    str_replace_all(arg.name, as.character(arg))
}
```

::: {.noteblock data-latex=""}
The source code of the [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L521) function is defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L521) script on _GitHub_.
:::
:::

@@

#### [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L525) Function {#func.msg.glue}
\

@@

The source code of the [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L525) function is shown below:
```{r eval=FALSE}
msg.glue <- function(msg_template, arg, arg.name = "%1"){
  msg_template |>
    msg.set_arg(arg, arg.name) |>
    str_glue()
}
```

::: {.noteblock data-latex=""}
The source code of the [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L525) function is defined in the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L525) script on _GitHub_.
:::
:::

@@

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section are available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
:::

@@

### Result RMSEs Table Functions
\

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section are available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
:::

@@

::: { #func.RMSE.Total_kable.args.RMSEs .sidebar }
  - ***RMSEs:*** The final _RMSEs Result Tibble_ to print;

@@

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section are available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R) script on _GitHub_.
:::

@@

::: {.noteblock data-latex=""}
The complete version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L74) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script on _GitHub_.
:::
:::

>>>>

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section are available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L445) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L445) script on _GitHub_.
:::

#### [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L448) Function {#func.clamp}
\

@@

The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L448) function is shown below:
```{r eval=FALSE}
clamp <- function(x, min = 0.5, max = 5) pmax(pmin(x, max), min)
```

::: {.noteblock data-latex=""}
The source code of the [clamp](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L448) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L445) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L448) script on _GitHub_.
:::
:::

#### [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L449) Function {#func.msg.set_arg}
\

@@

This function is a wrapper for the [stringr::str_replace_all](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace) `R` function, which is called internally to replace all occurrences of the pattern (placeholder) specified by the [arg_name](#func.msg.set_arg.args.arg.name) argument (`%1` by default), in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument with the value specified in the [arg](#func.msg.set_arg.args.arg) argument.
:::

@@

The character vector returned by the internally called [stringr::str_replace_all()](https://www.rdocumentation.org/packages/stringr/versions/1.5.0/topics/str_replace).
:::

@@

The source code of the [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L449) function is shown below:
```{r eval=FALSE}
msg.set_arg <- function(msg_template, arg, arg.name = "%1") {
  msg_template |> 
    str_replace_all(arg.name, as.character(arg))
}
```

::: {.noteblock data-latex=""}
The source code of the [msg.set_arg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L449) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L445) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L449) script on _GitHub_.
:::
:::

@@

#### [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L453) Function {#func.msg.glue}
\

@@

The source code of the [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#453) function is shown below:
```{r eval=FALSE}
msg.glue <- function(msg_template, arg, arg.name = "%1"){
  msg_template |>
    msg.set_arg(arg, arg.name) |>
    str_glue()
}
```

::: {.noteblock data-latex=""}
The source code of the [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L453) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L445) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L453) script on _GitHub_.
:::
:::

@@

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section are available in the [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L3) script on _GitHub_.
:::

@@

### Result RMSEs Tibble Functions
\

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section are available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) script on _GitHub_.
:::

@@

::: { #func.RMSE.Total_kable.args.RMSEs .sidebar }
  - ***RMSEs:*** The _Final RMSEs Result Tibble_ to print;

@@

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section are available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L78) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L78) script on _GitHub_.
:::

@@

::: {.noteblock data-latex=""}
The complete version of the source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L78) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script on _GitHub_.
:::
:::
